Democracy, Public Support, and Measurement Uncertainty

### 2021-08-13 paper/dcpo_demsupport.Rmd
revise text; add labels to appendices by hand

It is worth to note that, despite the great effort of collecting data and identifying differences, we could not reach a completely primary replication of @Claassen2020a's Dataverse materials.
Specifically, we have five fewer observations, three of which are no longer available in original survey data and two seem to have never existed, and one more survey item which was conflated in original data.
(See more details in Online Supplementary Material \@ref(dgp).)
Nevertheless, given there are over 2000 observations involved in the analysis, the five missing should not make a meaningful difference.

## Uncertainty Incorporation

Although measurement uncertainty has yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
Especially when measurement error is correlated with the outcome variable, the resulting bias could either attenuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, p.360; @caughey2018, p.254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, p. 18; @Gandhi2020, p. 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, pp. 791-792; @caughey2018, p. 254]. 
Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
We conduct inferences from the distributive data via a technique known as "method of composition" (MOC) [@Tanner1993, p.52;@Treier2008, p. 215; @caughey2018,p.A15-16].
See more details of the method and the operational process in Online Supplementary Material \@ref(moc).

@@

We also expanded Claassen's data pool assembling as much data on democratic support as possible from available opinion surveys around the world. 
The expansion ended with `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]

@@

Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries [@Claassen2020a, Model 1] in the left panel and separated by regime type (Model 2) on the right.
The uppermost set of results replicate @Claassen2020a without uncertainty.
The middle results introduce the uncertainty in the measurement of public support and democracy indices into the model.
And the lowermost set presents the results estimated with the expanded data with uncertainty.

@@

# Online Supplementary Materials {-}
# (APPENDIX) Appendix {-}
# Data Recollection and Uncertainty in Control Variables {#dgp}

@@

We also include measurement errors in control variables, including three democracy indices and corruption index.
We extracted the posterior distributions of democracy indices, including Liberal Democracy,electoral democracy index and liberal component index, which are provided by [@coppedge2018].
We drew 900 samples from the distribution of the Corruption Perception Index.
Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.

# DCPO Replication {#dcpo}

@@

# Replication with MOC Accounting for Uncertainty {#moc}

In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].

@@

We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, liberal component index, and corruption perceptions index.
For each of these five latent variables, we take 900 draws from its posterior distribution. We duplicate the dataset of variables “without” measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error, which yields 900 dataset.
In next step, we run each of analysis models with these 900 datesets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
We then draw one sample from the mulitivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
This procedure finally yields 900 samples of estimated coefficients drawn from the joint density of $\beta$ and $\theta$.
We calcluate point estimates and standard error based on these 900 samples.

>>>>

_It is worth to note that, despite the great effort of collecting data and identifying differences, we could not reach a completely primary replication of @Claassen2020a's Dataverse materials.
Specifically, we have five fewer observations, three of which are no longer available in original survey data and two seem to have never existed, and one more survey item which was conflated in original data.
(See more details in Online Supplementary Material \@ref(dgp).)
Nevertheless, given there are over 2000 observations involved in the analysis, the five missing should not make a meaningful difference._

## Incorporating Uncertainty

Although measurement uncertainty has yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can both attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @Blackwell2017a, 360-361].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254]. 
Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
We conduct inferences from the distributive data via a technique known as the "method of composition" (MOC) [@Tanner1993, 52; @Treier2008, 215; @caughey2018, A15-16].
See more details of the method and the operational process in Online Appendix C.

@@

## Adding Data

As a further test of the classic arguments on democracy and public support, we generated estimates of democratic support using the same procedure as in Claassen [-@Claassen2020a; -@Claassen2020b] on a bigger data set,  assembling as much survey data on democratic support as possible. We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]

@@

Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries [@Claassen2020a, 128, Model 1] in the left panel and democratic support separated by regime type (Model 2) on the right.
The uppermost set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty, and reproduce that article's findings.
The middle results introduce a single change: the uncertainty in the measurement of public support is taken into account.
In both models, the positive coefficients for democratic support are no longer statistically significant.
The uppermost set of results replicate @Claassen2020a without uncertainty.
The middle results introduce the uncertainty in the measurement of public support and democracy indices into the model.
And the lowermost set presents the results estimated with the expanded data with uncertainty.

@@

# Online Supplementary Materials {-}
# (APPENDIX) Appendix {-}
\setcounter{page}{1}
\renewcommand{\thepage}{A\arabic{page}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{A.\arabic{figure}}

# Data Recollection and Uncertainty in Control Variables {#dgp}

@@

We also include measurement errors in control variables, including three democracy indices and corruption index.
We extracted the posterior distributions of democracy indices, including Liberal Democracy, electoral democracy index and liberal component index, which are provided by [@coppedge2018].
We drew 900 samples from the distribution of the Corruption Perception Index.
Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.

# Appendix B: DCPO Replication {#dcpo}

@@

# Appendix C: The Method of Composition {#moc}

In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices, and corruption index (The latter one is included in APSR analyses).
Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].

@@

We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, liberal component index, and corruption perceptions index.
For each of these five latent variables, we take 900 draws from its posterior distribution. We duplicate the dataset of variables “without” measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error, which yields 900 dataset.
In next step, we run each of analysis models with these 900 datesets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
We then draw one sample from the mulitivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
This procedure finally yields 900 samples of estimated coefficients drawn from the joint density of $\beta$ and $\theta$.
We calculate point estimates and standard error based on these 900 samples.

# Appendix D: Secondary Models from Claassen (2020$a$, 2020$b$)
